%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LICENSE NOTICE (CC BY 4.0)
%
% Author/Creator: Alexander Menzel
% Copyright: 2025 MiraTherm
%
% This work is licensed under the Creative Commons Attribution 4.0 International License.
% License Text (URI): https://creativecommons.org/licenses/by/4.0/
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Planning}
\label{chap:Planning}

\section{Time plan}
\label{sec:Time plan}
%
The master project will presumably have the duration of 16 \acp{cw} with a pause of 2 \acp{cw} and will be divided into:

\begin{itemize}
    \item \acsp{cw} 44-45: Software requirements analysis.
    \item \acs{cw} 46: Software architecture design.
    \item \acs{cw} 47: Design of software interfaces.
    \item \acs{cw} 48: Implementation and tests of software drivers.
    \item \chdeleted[id=v1.0]{\acs{cw} 49: Motor Current Extremes Definition.}
    \item \acsp{cw} \chreplaced[id=v1.0]{49-51}{50-52}: Implementation\chdeleted[id=v1.0]{ and tests} of program logic.
    \item \chadded[id=v1.0]{52-02: Pause}
    \item \chadded[id=v1.0]{03-04: Integration tests and documentation.}
    \item \acsp{cw} \chreplaced[id=v1.0]{05-07}{01-03}: Paper writing.
    \item \acsp{cw} \chreplaced[id=v1.0]{08-09}{04-05}: Final review and submission of the paper.
\end{itemize}

Each calendar week will approximately consist of $\frac{150\unit{h}}{14} \approx 10.7$ hours of work.

\section{Responsibilities}
\label{sec:Responsibilities}

The whole work will be carried out by Alexander Menzel. The advisor for this master project will be Prof. Dr. Uwe Werner.

E-Mails and questions should be answered within 2 working days by both parties. If any problems arise, the advisor has to be informed as soon as possible.

\section{Deliverables}
\label{sec:Deliverables}
\chadded[id=v1.0]{The following deliverables are expected from this master project:}
\begin{itemize}
    \item \chadded[id=v1.0]{\textbf{Software Specification Document}: This document.}
    \item \chadded[id=v1.0]{\textbf{Software Source Code inkl. Comments}: The complete source code of the radiator thermostat software, including in-line comments and documentation. If needed, markdown files explaining the code structure and usage will be provided in the source code repository.}
    \item \chadded[id=v1.0]{\textbf{Software Architecture, Design and Test Documentation}: Documentation detailing the software architecture, design decisions, and test procedures/results. It is allowed to use markdown files for this purpose as well.}
    \item \chadded[id=v1.0]{\textbf{Final Master Project Paper}: A detailed paper in the form of an \ac{ieee} report summarizing the entire master project. It should include references to all relevant documents and materials produced during the project.}
\end{itemize}